A Plasma Torus Around a Young Low-Mass Star

### 2025-01-20 paper/ms.tex
update

\begin{table*}
\scriptsize
\setlength{\tabcolsep}{2pt}
\centering
\caption{Selected System Parameters for TIC~141146667}
\label{tab:params}
\begin{tabular}{llcc}
\hline \hline
Parameter & Description & Value & Source\\
\hline 
%
$T_{\rm eff}$\dotfill                   & Effective Temperature (K) \hspace{9pt}\dotfill                 & 2972 $\pm$ 40    & 1 \\
%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & 4.53 $\pm$ 0.05  & 6 \\
$R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
%
$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  & 6 \\
%
Age                                     & Adopted stellar age (Myr)\dotfill                              & YYY  & 8 \\
%
Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & X \\
%
$P_{\rm rot}$\dotfill                   & Rotation period (hr)\dotfill                                   & $3.930\pm 0.001$ & X \\
%
$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & - \\
                                        & \hspace{3pt} ($2\pi R_\star/P_{\rm rot}$) (\kms)	             &                      \\
%
$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  128$\pm$3       & X \\
                                        & \hspace{3pt} velocity (\kms)	                                 &                      \\
%
$i_\star$\dotfill                       & Stellar inclination (deg)\dotfill                              & 	XXX             & X \\
%
$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.6 \pm X.X$   & X \\
%
$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   &  XXX             & X \\
                                        & \hspace{3pt} radius ($R_\star$)	                               &                      \\
%
$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & X \\
$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & X \\
%
$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  X.X             & Y \\ 
                                        & \hspace{3pt} equivalent width (\AA)	                           &                      \\
Range(EW$_{\rm H\alpha}$)$_1$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
                                        & \hspace{3pt} from Clump 1 (\AA)	                               &                      \\
Range(EW$_{\rm H\alpha}$)$_2$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
                                        & \hspace{3pt} from Clump 2 (\AA)	                               &                      \\
\hline
\end{tabular}
\begin{flushleft}
\footnotesize{ \textsc{NOTE}---
%$^\dagger$ The GAIADR2 and GAIAEDR3 identifiers for Kepler 1627A are identical.  The secondary
is not resolved in the Gaia point source catalog.
$^*$ Given only $v\sin i$ and $2\pi R_\star/P_{\rm rot}$, $\cos i=0.11^{+0.11}_{-0.08}$.
Provenances are:
1: SED fit\cite{Bouma2024},
%$^6$Cluster isochrone (MIST adopted; PARSEC compared for quoted
%  uncertainty),
2: TESS light curve,
%  3: HIRES spectra and specmatch(?),
%$^8$Pre-main-sequence CAMD interpolation (Section~\ref{sec:camd}),
}
\end{flushleft}
\vspace{-0.5cm}
\end{table*}

@@

\section{Observations}

@@

{\bf TESS:}

{\bf Keck/HIRES:}
We observed using the standard setup and reduction techniques of the
California Planet Survey \cite{Howard2010}.
Winds of 30 mph contributed to
1\farcs2$\pm$0\farcs2 seeing over the spectroscopic observations.

\section{Data Reduction}

\section{Modeling the Emitting Clump}
\label{subsec:model}

>>>>

\begin{table*}
\scriptsize
\setlength{\tabcolsep}{2pt}
\centering
\caption{Selected System Parameters for TIC~141146667}
\label{tab:params}
\begin{tabular}{llcc}
\hline \hline
Parameter & Description & Value & Source\\
\hline 
%
$T_{\rm eff}$\dotfill                   & Effective Temperature (K) \hspace{9pt}\dotfill                 & 2972 $\pm$ 40    & 1 \\
%
%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & YYY              & X \\
%
$R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
%
$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  & 6 \\
%
Age                                     & Adopted stellar age (Myr)\dotfill                              & YYY  & 8 \\
%
Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & X \\
%
$P_{\rm rot}$\dotfill                   & Rotation period (hr)\dotfill                                   & $3.930\pm 0.001$ & X \\
%
$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & - \\
                                        & \hspace{3pt} ($2\pi R_\star/P_{\rm rot}$) (\kms)	             &                      \\
%
$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  128$\pm$3       & X \\
                                        & \hspace{3pt} velocity (\kms)	                                 &                      \\
%
$i_\star$\dotfill                       & Stellar inclination (deg)\dotfill                              & 	XXX             & X \\
%
$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.6 \pm X.X$   & X \\
%
$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   &  XXX             & X \\
                                        & \hspace{3pt} radius ($R_\star$)	                               &                      \\
%
$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & X \\
$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & X \\
%
$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  X.X             & Y \\ 
                                        & \hspace{3pt} equivalent width (\AA)	                           &                      \\
Range(EW$_{\rm H\alpha}$)$_1$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
                                        & \hspace{3pt} from Clump 1 (\AA)	                               &                      \\
Range(EW$_{\rm H\alpha}$)$_2$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
                                        & \hspace{3pt} from Clump 2 (\AA)	                               &                      \\
\hline
\end{tabular}
\begin{flushleft}
\footnotesize{ \textsc{NOTE}---
%$^\dagger$ The GAIADR2 and GAIAEDR3 identifiers for Kepler 1627A are identical.  The secondary
is not resolved in the Gaia point source catalog.
$^*$ Given only $v\sin i$ and $2\pi R_\star/P_{\rm rot}$, $\cos i=0.11^{+0.11}_{-0.08}$.
Provenances are:
1: SED fit\cite{Bouma2024},
%$^6$Cluster isochrone (MIST adopted; PARSEC compared for quoted
%  uncertainty),
2: TESS light curve,
%  3: HIRES spectra and specmatch(?),
%$^8$Pre-main-sequence CAMD interpolation (Section~\ref{sec:camd}),
}
\end{flushleft}
\vspace{-0.5cm}
\end{table*}

@@

\subsection{Observations \& Data Reduction}

@@

{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15, 21, 41, 48,
and 75.  Two-minute data were acquired during Sectors 41, 48 (TESS
DDT039, PI: M.~Kunimoto), and 75 (TESS Program G06030, PI: L.~Bouma);
the earlier data had a 30-minute cadence, which significantly
phase-smears sharp features over a $<$4\,hour period (see
\cite{Gunther2022}).
The nearest star in the TESS images, TIC~141146666 ($T$14.5), is 
25$''$ from TIC~141146667 and does not appear to photometrically vary.

{\it Keck/HIRES:}
We observed using the standard setup and reduction techniques of the
California Planet Survey \cite{Howard2010}.
Winds of 30 mph contributed to
1\farcs2$\pm$0\farcs2 seeing over the spectroscopic observations.  
% TODO: mention deblazing 20241115_tic1411_deblazing_notes.txt

\subsection{Stellar Parameters}
{\it Age}
While most CPVs can be spatially and kinematically associated with known young
moving groups using tools such as BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018},
TIC~141146667 cannot \cite{Bouma2024}.
%.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
%git commit \texttt{394b486}}

Isochrone age: $\sim$TucHor or younger.  Maybe 30-35myr?
NB color puts it at ~M4.5 (main seq).
BP-RP=3.3..

Lithium?
Frankly, it's not obviously there!  (but maybe this is bc of the blending, and
a pEW would show smth small)
% We have K=10.47, d=57pc - > DM ~= 3.78 -> M_K ~= 6.67
Figure7 of Wood23 suggests from the Feiden Li depletion curves that no lithium would imply $t$>37Myr.
However Figure5 frmo the same work suggests maybe try binning up the spectrum, and then comparing against Bochanski+2007 for a lithium-free template.

This is weird.  Are you 100\% sure it's not a binary?  Ups the need for
the RV analysis.

{\it Effective temperature, radius, and mass}
We adopt the results from the spectral energy distribution fitting
exercise described by \cite{Bouma2024}.
In brief, this approach used
\texttt{astroARIADNE}...
\cite{Vines2022} with the BT-Settl stellar
atmosphere models \cite{Allard2012} assuming the
\cite{Asplund2009} solar abundances, and the
\cite{Barber2006} water line lists.  
We used broadband magnitudes from Gaia DR2, APASS, 2MASS, SDSS, and WISE
  $W1$ and $W2$.  (explain)...
%%%%%%%%
%\texttt{astroARIADNE} compares the measured broadband flux
%measurements against pre-computed model grids, and by default fits for
%six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
%Fe/H}], d \}$.  The distance  prior is drawn from
%\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
%generally unconstrained.  Given our selection criteria for the stars,
%we assumed the following priors for the temperature, stellar size, and
%extinction:
%\begin{align}
%  T_{\rm eff} / {\rm K}    &\sim \mathcal{U}(2000, 8000), \\
%  R_\star / R_\odot  &\sim \mathcal{U}(0.1, 1.5), \\
%  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
%\end{align}
%for \deleted{$\mathcal{N}$ the Gaussian and }$\mathcal{U}$ the uniform
%distribution\deleted{s, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
%truncated normal distribution with mean $\mu$, standard deviation
%$\sigma$, and lower and upper bounds $a$ and $b$}.  We validated our
%chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
%Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
%sampled the posterior probability assuming the default Gaussian
%likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
%0.01$, where $\mathcal{Z}$ denotes the evidence.

{\it Binarity}

\subsection{Spectral Behavior of Other Lines}

First, chromospheric:

{\it H$\gamma$, H$\delta$}
Line ratios.

{\it Ca [K]}
{\it Also} shows some high-velocity emission.  So, the emitting material has
calcium ions.

{\it He 5880}
Also variable...

{\it Magnesium b orders}
Shows some variability that is horrendously blended.

{\it K[I] 7700}
Literally the only obvious photospheric line.

\subsection{Modeling the Emitting Clump}
\label{subsec:model}
